 

### 2020-12-07 doc/manuscript/Dow_manuscript.Rmd
writing- results

Similarly, annual growth recorded in tree-ring records, $RW$, rarely displayed a significant correlation to spring  $T_{max}$ (Fig. `r tree_rings` or  $T_{min}$ (Fig. `r tree_rings_TMIN`).

@@

@@

# Acknowledgements
people: (everyone who helped collect data), Jess Shue (data)
Funding: ForestGEO

>>>>

Similarly, between species-level residual chronologies rarely exhibited significant correlations to either $T_{max}$ or $T_{min}$ in the months corresponding to the critical temperature windows identified here (Figs. `r tree_rings`, `r tree_rings_TMIN`).
Although correlations were rarely significant, there was a consistent pattern in responses to $T_{max}$ across all species at both sites:
responses to $T_{max}$ were negative or neutral in all months from February to August, with the exception of one spring month at each site (April at SCBI, May at Harvard Forest) where growth displayed a positive or neutral responses to $T_{max}$ (Fig. `r tree_rings`).
In these months, positive correlations to $T_{max}$ were statistically significant (at p=0.05) for one of nine ring-porous species at SCBI and one of two diffuse-porous species at each site.
In the prior months, the generally negative correlations to $T_{max}$ were not significant, excepting significant correlations of one species at each site  (ring-porous *Carya tomentosa* in March at SCBI; diffuse-porous *Acer rubrum* in April at Harvard Forest).
Starting in May at SCBI, significant correlations to $T_{max}$ were common, occurring for nine of the eleven species in May and 3-7 species for each month June through August.
At Harvard Forest, there was only one statistically significant negative correlation to post-May $T_{max}$ (*Quercus rubra* in June).

@@

Patterns in $T_{min}$ were fairly similar to those of $T_{max}$, but weaker and more stochastic, with more (non-significant) correlations going in opposite directions (Fig. `r tree_rings_TMIN`). 
There were no significant correlations to $T_{min}$ prior to May at SCBI or June at Harvard Forest.

@@

# Acknowledgements
people: (everyone who helped collect data-- see list on GitHub), Jess Shue (data)
Funding: ForestGEO

### 2020-12-07 doc/manuscript/tables_figures/tables.Rmd
writing- results

\newpage
```{r species_table, eval=TRUE, echo=FALSE, warning=FALSE}
library(knitr)
library(kableExtra)
species_table <- read.csv(file = "species_table.csv", col.names = c("site", "xylem porosity","species", "species code", "n trees", "n tree-years", "n cores", "date range"),  stringsAsFactors = FALSE, check.names = FALSE)
kable(species_table, caption = "Table 2. Dominant ring- and diffuse-porous species at SCBI and Harvard Forest analyzed here, along with sample sizes.",  format = "latex", booktabs = TRUE,  escape = F) %>%
add_header_above(c(" ", " ", " ", " ", "dendrometer bands" = 2, "tree cores"=2 )) %>%
kable_styling(latex_options = c("scale_down", "hold_position"), protect_latex = T) 
```

>>>>

\newpage
```{r species_table, eval=TRUE, echo=FALSE, warning=FALSE}
library(knitr)
library(kableExtra)
species_table <- read.csv(file = "species_table.csv", col.names = c("site", "xylem porosity","species", "species code", "n trees", "n tree-years", "n cores", "date range"),  stringsAsFactors = FALSE, check.names = FALSE)
kable(species_table, caption = "Table 2. Dominant ring- and diffuse-porous species at the Smithsonian Conservation Biology Institute (SCBI) and Harvard Forest, along with sample sizes analyzed here.",  format = "latex", booktabs = TRUE,  escape = F) %>%
add_header_above(c(" ", " ", " ", " ", "dendrometer bands" = 2, "tree cores"=2 )) %>%
  pack_rows("", 1, 9, latex_gap_space = "1em", colnum = 4, hline_before = FALSE) %>%
  pack_rows("", 10, 11, latex_gap_space = "1em", colnum = 4, hline_before = FALSE) %>%
  pack_rows("", 12, 14, latex_gap_space = "1em", colnum = 4, hline_before = FALSE) %>%
  pack_rows("", 15, 22, latex_gap_space = "1em", colnum = 4, hline_before = FALSE) %>%
kable_styling(latex_options = c("scale_down", "hold_position"), protect_latex = T) 
```
